Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-08 ms.tex
more on three parameter fits
more on f_1 prior

\begin{equation}
\mathcal{L}(\{I\}|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
\end{equation}

@@

\begin{equation}
P(T_2) = \mathcal{N}(T_2|\bar{T}_2, \sigma_{\bar{T}_2})
\end{equation}

@@

>>>>

\begin{equation} \label{equ:like}
\mathcal{L}(\{I\}|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
\end{equation}

@@

\begin{equation} \label{equ:t2prior}
P(T_2) = \mathcal{N}(T_2|\bar{T}_2, \sigma_{\bar{T}_2})
\end{equation}

@@

We still employ the likelihood function of Equation \ref{equ:like}, the only
difference being that $f_1$ can vary from proposal to proposal within each 
individual pixel when predicting \{$\tilde{I}_{\nu_i}$\} with Equation 
\ref{eqn:inten}. The prior $P(T_2)$ from Equation \ref{equ:t2prior} remains 
unchanged. The prior on $f_1$ is:

\begin{equation} \label{equ:f1prior}
P(f_1) = \mathcal{N}(f_1|\bar{f}_1, \sigma_{\bar{f}_1})
\end{equation}

With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
stringent prior, but we must restrict the fit from wandering with too much
freedom, as we are attempting to constrain three parameters using an SED
with only seven intensity measurements.

% add comment about high f_1 regions near NGP
